\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\author{OC3 Board}
\title{Open Content Creation Club: Constitution}

\renewcommand{\thesection}{Article \Roman{section}}

\begin{document}
	\maketitle
	
	\section{Name}
	\begin{enumerate}[label=(\alph*)]
		\item The full name of this club is ``The Open Content Creation Club'', and this name will be used in all instances in which the full club name is required.
		\item The club can also be referred to as ``The OC3'', ``The OpenC3'', or ``The OpenCCC'' in cases where it is unnecessary to display the full club name.
	\end{enumerate}
	
	\section{Purpose}
	The Open Content Creation Club's purpose is to demonstrate students' ability to create new media such as images, videos, text, and \emph{content} with non-commercial software---software that is \emph{free}, as in ``the users have the \emph{freedom} to run, copy, distribute, study, change and improve the software'' (GNU Free Software Definition)---software that is and will continue to be accessible by anyone.
	
	\section{Membership}
	\begin{enumerate}[label=(\alph*)]
		\item All persons are eligible to become club members.
		\item Persons are considered members only if the board has listed them on the club roster for the current year.
	\end{enumerate}
	
	\section{Dues}
	\begin{enumerate}[label=(\alph*)]
		\item Members will have \textbf{no mandatory dues}.
		\item The board may ask for donations not exceeding \$5.00 per semester to help pay for club services such as online servers used to organize and provide project resources to club members.
	\end{enumerate}
	
	\section{Board}
	The Open Content Creation Club will have the following board positions:
	\begin{enumerate}[label=(\alph*)]
		\item \emph{President}, expected to organize club meetings and calendars
		\item \emph{Vice President}, expected to assist the President in completing their tasks
		\item \emph{Secretary}, expected to track attendance at club meetings and to turn in club minutes on time for every club meeting
		\item \emph{Underclassmen Representative}, expected to represent underclassmen in club decision making, must be a freshman or sophomore
		\item Any number of \emph{General Board Members}, expected to assist professional board members (President, Vice President, Secretary, and Underclassmen Representative) in completing their tasks and to participate in club decision making
	\end{enumerate}
	
	\section{Amendments}
	A club must be a dynamic organization, and the existence of amendments reflect this need.
	Amendments can be appended to this constitution when a majority of \emph{voting power} agrees to pass an amendment.
	Voting power is distributed as such:
	\begin{enumerate}[label=(\alph*)]
		\item The first half of the voting power is split evenly among the current board members.
		\item The second half of the voting power is split evenly among the club members.
	\end{enumerate}
	
\end{document}